\documentclass[12pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{charter}
\usepackage{hyperref}

\begin{document}
\pagestyle{empty}

\hfill \today

\noindent
\textbf{To:} \\
The Editor-in-Chief \\
Elsevier Journal Editorial Board \\

\vspace{1.5em}

\noindent
\textbf{Subject: Submission of original research manuscript for publication}

\vspace{1.5em}

\noindent
Dear Editor, \\

\vspace{1em}
\noindent
We are pleased to submit our original research manuscript titled \textbf{``Verification-Guided Retrieval-Augmented Generation for Reliable Semiconductor Device Physics Reasoning''} for consideration for publication as a regular research article.

\vspace{1em}
\noindent
In this study, we address the challenge of scientific reasoning in large language models (LLMs) when applied to semiconductor device physics. We introduce a novel neuro-symbolic retrieval-augmented generation (RAG) framework that couples a domain-adapted sub-billion parameter model with a deterministic three-stage physical validation layer (consisting of symbolic parsing, dimensional consistency check, and multi-node numerical plausibility bounds). Our results show that our framework improves the physical correctness score of the small model on a stratified 100-question semiconductor benchmark from 1.05 to 2.95 (on a 0--4 scale), outperforming larger cloud-hosted models.

\vspace{1em}
\noindent
We believe that this work falls directly within the scope of your journal, as it contributes to the development of trustworthy and resource-efficient scientific AI systems.

\vspace{1em}
\noindent
We confirm that this manuscript is original, has not been published before, and is not currently under consideration for publication elsewhere. All authors have read and approved the manuscript for submission.

\vspace{1.5em}
\noindent
Thank you for your time and consideration of our work.

\vspace{1.5em}
\noindent
Sincerely, \\
\textbf{G Veena} (Corresponding Author) \\
School of Computing, Amrita Vishwa Vidyapeetham \\
Kollam, Kerala, India \\
Email: veenag@am.amrita.edu \\

\end{document}
